Exploring the structure of the bound proton with Deeply Virtual Compton Scattering

### 2019-02-21 eg6-letters/incoherent/incoherent_prl.tex
minor cleaning for publication
Add notes from Stepan and Raphael

\RequirePackage{lineno}
\documentclass[twocolumn,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%
\def\Dirac#1{#1\hskip-5pt/}
%
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
\expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
\expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
\renewenvironment{#1}%
{\linenomath\csname old#1\endcsname}%
{\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
\patchAmsMathEnvironmentForLineno{#1}%
\patchAmsMathEnvironmentForLineno{#1*}}%
\AtBeginDocument{%
\patchBothAmsMathEnvironmentsForLineno{equation}%
\patchBothAmsMathEnvironmentsForLineno{align}%
\patchBothAmsMathEnvironmentsForLineno{flalign}%
\patchBothAmsMathEnvironmentsForLineno{alignat}%
\patchBothAmsMathEnvironmentsForLineno{gather}%
\patchBothAmsMathEnvironmentsForLineno{multline}%
}

\begin{document}
\linenumbers

\title{Deeply Virtual Compton Scattering measurement off bound protons}

@@

\date{\today}
\begin{abstract}
 We report the first beam spin asymmetry (BSA) measurement of incoherent deeply 
   virtual Compton scattering (DVCS) off $^4$He. The data were accumulated 
   using a 6 GeV longitudinally polarized electron beam incident on a 
   pressurized $^4$He gaseous target placed within the CLAS spectrometer in 
   Hall-B at the Thomas Jefferson National Accelerator Facility. The azimuthal 
   angle ($\phi$) dependence of the BSA was studied in a wide range of virtual 
   photon and scattered proton kinematics. The $Q^2$, $x_B$, and $t$ 
   dependencies of the BSA on the bound proton are compared with those on the 
   free proton. In the whole kinematical region of our measurements, the BSA on 
   the bound proton is smaller by $20\%$ to $40\%$, indicating possible medium 
   modification of its partonic structure. This measurement opens a new avenue 
   for studying the structure of bound nucleons and for exploring the origin of 
   the EMC effect using the framework of the generalized parton distributions.

\end{abstract}
\pacs{Valid PACS appear here}

@@

The two main backgrounds that contributed to the event sample after the 
exclusivity cuts are due to accidental coincidences and exclusive $\pi^0$ 
production where one of the photons from the $\pi^0$ decay escapes detection.  
The contribution from accidental events, i.e., $e'p'\gamma$ collections with 
particles originating from different electron scatterings, was evaluated to be 
6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated using detector 
simulation and experimental data. From simulation, we calculated the ratio ($R 
= N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that 
were wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$.  
Then in each kinematical bin and for each beam-helicity state, the 
$\pi^0$-subtracted experimental DVCS events were calculated as $N = 
N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
($ep\rightarrow e'p'\pi^0$) events. Depending on the kinematics, we found this 
contamination to be 8 to 10\%.

@@

%conclusion
In summary, we have presented the first BSA measurement associated with bound 
proton DVCS off $^4$He using an upgraded setup of the CLAS spectrometer at 
Jefferson Lab. Our results are compared to model calculations based on 
different assumptions of the nuclear medium effects at the partonic level. The 
bound-proton BSA is largely suppressed compared to the free proton BSA. This 
result is a first step in using a novel experimental method of understanding 
the properties of bound nucleons directly from the basic degrees of freedom of 
QCD, quarks and gluons.

>>>>

\RequirePackage{lineno}
\documentclass[twocolumn,nofootinbib,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%
\def\Dirac#1{#1\hskip-5pt/}
%
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
\expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
\expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
\renewenvironment{#1}%
{\linenomath\csname old#1\endcsname}%
{\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
\patchAmsMathEnvironmentForLineno{#1}%
\patchAmsMathEnvironmentForLineno{#1*}}%
\AtBeginDocument{%
\patchBothAmsMathEnvironmentsForLineno{equation}%
\patchBothAmsMathEnvironmentsForLineno{align}%
\patchBothAmsMathEnvironmentsForLineno{flalign}%
\patchBothAmsMathEnvironmentsForLineno{alignat}%
\patchBothAmsMathEnvironmentsForLineno{gather}%
\patchBothAmsMathEnvironmentsForLineno{multline}%
}

\begin{document}
%\linenumbers

\title{Exploring the structure of the bound proton with Deeply Virtual Compton Scattering}

@@

\date{\today}
\begin{abstract}
In the past two decades, deeply virtual Compton scattering of electrons has been successfully 
used to advance our knowledge of the partonic structure of the free proton and investigate 
correlations between the transverse position and the longitudinal momentum of quarks inside 
the nucleon. In this work, we report the first beam spin asymmetry (BSA) measurement of deeply 
virtual Compton scattering (DVCS) off a proton bound in $^4$He. The structure of the bound 
nucleons in nuclei has been studied in inclusive deep-inelastic lepton scattering experiments 
off nuclear targets only, showing a significant difference in longitudinal momentum distribution 
of quarks inside the bound nucleon, known as the EMC effect and still eluding our understanding. 
The data used here were accumulated using a $6$ GeV longitudinally polarized electron beam 
incident on a pressurized $^4$He gaseous target placed within the CLAS spectrometer in Hall-B 
at the Thomas Jefferson National Accelerator Facility. The azimuthal angle ($\phi$) dependence 
of the BSA was studied in a wide range of virtual photon and scattered proton kinematics. The 
Q$^2$, x$_B$, and t dependencies of the BSA on the bound proton are compared with those on the 
free proton. In the whole kinematical region of our measurements, the BSA on the bound proton 
is smaller by 20\% to 40\%, indicating possible medium modification of its partonic structure.
\end{abstract}
%\pacs{Valid PACS appear here}

@@

The two main backgrounds that contributed to the event sample after the 
exclusivity cuts are due to accidental coincidences and exclusive $\pi^0$ 
production where one of the photons from the $\pi^0$ decay escapes detection.  
The contribution from accidental events, i.e., $e'p'\gamma$ collections with 
particles originating from different electron scatterings, was evaluated to be 
6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated and substracted using detector 
simulation and experimental data. From simulation, we calculated the ratio ($R 
= N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that 
were wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events ($N^{1\gamma}_{sim}$) to the 
number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$ ($N^{2\gamma}_{sim}$).  
Then in each kinematical bin and for each beam-helicity state, the 
$\pi^0$-subtracted experimental DVCS events were calculated as $N = 
N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
($ep\rightarrow e'p'\pi^0$) events. Depending on the kinematics, we substracted
between 8 and 10\% of the data due to the $\pi^0$ contamination.

@@

%conclusion
In summary, we have presented the first BSA measurement associated with bound 
proton DVCS off $^4$He using an upgraded setup of the CLAS spectrometer at 
Jefferson Lab. Our results are compared to model calculations based on 
different assumptions of the nuclear medium effects at the partonic level. The 
bound-proton BSA is largely suppressed compared to the free proton BSA. This 
result is a first step in using a novel experimental method of understanding 
the properties of bound nucleons directly from the basic degrees of freedom of 
QCD, quarks and gluons. Planned experiments at Jefferson Lab will continue 
and extend these studies of the bound nucleon structure using DVCS. We have 
an experimental program using the CLAS12 detector in the experimental Hall-B, 
called ALERT, to improve the DVCS measurements with the detection of nuclear
fragments to control better the final state interactions and the initial state
kinematic.
